### 2020-11-30 doc/manuscript/Dow_manuscript.Rmd
bit of work on manuscript

```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
mean_growth_parameters <- read.csv("tables_figures/mean_growth_parameters.csv",stringsAsFactors = FALSE, check.names = FALSE)
knitr::kable(mean_growth_parameters) 
```

@@

At SCBI, ring-porous $DOY_{25}$ and $DOY_{50}$ shifted back while ${DOY_75}$ did not shift, resulting in an extended peak growing season length when critical window temperatures were warmer (Tables `r hypothesis_table`, Figs. `r pheno_Tsensitivity`, `r DOYtiming`).
Diffuse-porous $DOY_{25}$, $DOY_{50}$, and ${DOY_75}$ shifted back uniformly resulting in no significant change in peak growing season length. At Harvard Forest, ring-porous ${DOY_75}$ shifted back faster than ${DOY_25}$, resulting in shorter peak growins season length, while diffuse-porous ${DOY_25}$ shifted back faster than ${DOY_75}$, resulting in an extended peak growing season length in response to warmer critical window temperatures.

@@

Total annual growth, $\Delta DBH$, also was not consistently linked to early spring temperatures, displaying either no relationship (SCBI) or extremely small changes (Harvard Forest) (Tables `r hypothesis_table`, Fig. `r pheno_Tsensitivity`).

>>>>

\newpage
```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
mean_growth_parameters <- read.csv("tables_figures/mean_growth_parameters.csv",stringsAsFactors = FALSE, check.names = FALSE)
knitr::kable(mean_growth_parameters) 
```

@@

At SCBI, ring-porous $DOY_{25}$ and $DOY_{50}$ shifted earlier while ${DOY_75}$ did not shift, resulting in longer peak growing season length when critical window temperatures were warmer (Tables `r hypothesis_table`, Figs. `r pheno_Tsensitivity`, `r DOYtiming`).
Diffuse-porous $DOY_{25}$, $DOY_{50}$, and ${DOY_75}$ shifted earlier uniformly resulting in no significant change in peak growing season length. 
At Harvard Forest, ring-porous ${DOY_75}$ shifted more than ${DOY_25}$, resulting in shorter peak growing season length, while diffuse-porous ${DOY_25}$ shifted more than ${DOY_75}$, resulting in an extended peak growing season length in response to warmer critical window temperatures.

@@

Total annual growth measured with dendrometer bands, $\Delta DBH$, also was not consistently linked to early spring temperatures, displaying either no relationship (SCBI) or extremely small changes (Harvard Forest) (Tables `r hypothesis_table`, Fig. `r pheno_Tsensitivity`).

Annual growth recorded in tree-ring records, $RW$, ...
